\bigskip

\begin{theorem} \label{thm:ArbitraryUnionOfOpenSetsIsOpen}
    Let $(X, d)$ be a metric space. Let $E_{y} \subseteq X$ be an open set for each $y \in Y$. Then we have
    \[
    \bigcup_{y \in Y} E_{y} \text{ is open}
    \]
    whether $Y$ is finite, countable, or uncountable. This theorem states that an arbitrary union of open sets is open.
\end{theorem}

\begin{proof}
    Let $p \in \displaystyle \bigcup_{y \in Y} E_{y}$ be given. Then there exists some $y_{0} \in Y$
    such that $p \in E_{y_{0}}$. Since $E_{y_{0}}$ is open, there exists some $r \in \R^{+}$
    such that $N_{r}(p) \subseteq E_{y_{0}}$. Then we have
    \[
    N_{r}(p) \subseteq E_{y_{0}} \subseteq \bigcup_{y \in Y} E_{y},
    \]
    which implies that $p$ is an interior point of $\displaystyle \bigcup_{y \in Y} E_{y}$.
    Since $p$ is arbitrary, $\displaystyle \bigcup_{y \in Y} E_{y}$ is open.
\end{proof}

\bigskip

\begin{corollary} \label{cor:ArbitraryIntersectionOfClosedSetsIsClosed}
    Let $(X, d)$ be a metric space. Let $E_{y} \subseteq X$ be a closed set for each $y \in Y$. Then we have
    \[
    \bigcap_{y \in Y} E_{y} \text{ is closed}
    \]
    whether $Y$ is finite, countable, or uncountable. This corollary states
    that an arbitrary intersection of closed sets is closed.
\end{corollary}

\begin{proof}
    By \Cref{cor:ClosedSetComplementIsOpenSet}, $(E_{y})^{c}$ is open for each $y \in Y$.
    Then, by \Cref{thm:ArbitraryUnionOfOpenSetsIsOpen}, we have
    \[
    \bigcup_{y \in Y} (E_{y})^{c} \text{ is open.}
    \]
    By \Cref{thm:OpenSetComplementIsClosedSet}, we have
    \[
    \bigcap_{y \in Y} E_{y} = \paren*{\bigcup_{y \in Y} (E_{y})^{c}}^{c} \text{ is closed.}
    \]
\end{proof}

\bigskip

\begin{theorem} \label{thm:FiniteIntersectionOfOpenSetsIsOpen}
    Let $(X, d)$ be a metric space. Let $E_{1}, E_{2}, \dots, E_{n} \subseteq X$
    be open sets for some $n \in \N$. Then we have
    \[
    \bigcap_{k = 1}^{n} E_{k} \text{ is open.}
    \]
    This theorem states that a finite intersection of open sets is open.
\end{theorem}

\begin{proof}
    Let $p \in \displaystyle \bigcap_{k = 1}^{n} E_{k}$ be given. Then we have $p \in E_{j}$ for all $j = 1, 2, \dots, n$.
    Since $E_{j}$ is open, there exists some $r_{j} \in \R^{+}$ such that $N_{r_{j}}(p) \subseteq E_{j}$ for each $j = 
    1, 2, \dots, n$. Let $R$ be a set defined by
    \[
    R \coloneqq \setbuilder*{r_{j}}{j = 1, 2, \dots, n} \subseteq \R^{+}.
    \]
    Let $f: J_{n} \to R$ be a function defined by
    \[
    f(j) = r_{j}.
    \]
    Then $f$ is surjective. By \Cref{lem:SubsetOfJnIsFinite,thm:SurjectionFromFiniteSetIsFinite}, $R$ is finite.
    Then, by \Cref{thm:FiniteOrderedSetHasExtremum}, $R$ has a minimum element, say $r = \min R > 0$. Then we have
    \[
    N_{r}(p) \subseteq N_{r_{j}}(p) \subseteq E_{j} \text{ for all } j = 1, 2, \dots, n
    \implies N_{r}(p) \subseteq \bigcap_{k = 1}^{n} E_{k},
    \]
    which implies that $p$ is an interior point of $\displaystyle \bigcap_{k = 1}^{n} E_{k}$.
    Since $p$ is arbitrary, $\displaystyle \bigcap_{k = 1}^{n} E_{k}$ is open.
\end{proof}

\bigskip

\begin{corollary} \label{cor:FiniteUnionOfClosedSetsIsClosed}
    Let $(X, d)$ be a metric space. Let $E_{1}, E_{2}, \dots, E_{n} \subseteq X$
    be closed sets for some $n \in \N$. Then we have
    \[
    \bigcup_{k = 1}^{n} E_{k} \text{ is closed.}
    \]
    This corollary states that a finite union of closed sets is closed.
\end{corollary}

\begin{proof}
    By \Cref{cor:ClosedSetComplementIsOpenSet}, $(E_{k})^{c}$ is open for each $k = 1, 2, \dots, n$.
    Then, by \Cref{thm:FiniteIntersectionOfOpenSetsIsOpen}, we have
    \[
    \bigcap_{k = 1}^{n} (E_{k})^{c} \text{ is open.}
    \]
    By \Cref{thm:OpenSetComplementIsClosedSet}, we have
    \[
    \bigcup_{k = 1}^{n} E_{k} = \paren*{\bigcap_{k = 1}^{n} (E_{k})^{c}}^{c} \text{ is closed.}
    \]
\end{proof}

\bigskip

\begin{definition} \label{def:Closure}
    Let $(X, d)$ be a metric space and $E \subseteq X$. Let $E'$ be the set of all limit points of $E$.    
    The \textbf{closure} of $E$, which is denoted by $\overline{E}$, is defined by
    \[
    \overline{E} \coloneqq E \cup E'.
    \]
\end{definition}

\bigskip

\begin{theorem} \label{thm:PropertiesOfClosure}
    Let $(X, d)$ be a metric space and $E \subseteq X$. Then we have the following properties:
    \begin{enumerate}[label=\textbf{(\Alph*)}]
        \item $\overline{E}$ is closed.
        \item $E = \overline{E} \iff E$ is closed.
        \item For any closed subset $F \subseteq X$ such that $E \subseteq F$, we have $\overline{E} \subseteq F$.
    \end{enumerate}
    \textbf{(C)} states that the closure of $E$ is the smallest closed set containing $E$.
\end{theorem}

\begin{proof}
    \begin{enumerate}[label=\textbf{(\Alph*)}]
        \item We will show that $\paren*{\overline{E}}^{c}$ is open. Let $p \in \paren*{\overline{E}}^{c}$ be given.
        Since $p \notin E$ and $p \notin E'$, there exists some $r \in \R^{+}$ such that
        \[
        E \cap Q_{r}(p) = \emptyset \implies E \cap N_{r}(p) = \emptyset \implies N_{r}(p) \subseteq E^{c}.
        \]
        By \Cref{thm:NeighborhoodIsOpen}, $N_{r}(p)$ is open. Then, for any $q \in N_{r}(p)$,
        there exists $\veps \in \R^{+}$ such that
        \begin{align*}
            N_{\veps}(q) \subseteq N_{r}(p) \subseteq E^{c}
            \implies &E \cap N_{\veps}(q) = \emptyset \\
            \implies &E \cap \paren*{Q_{\veps}(q) \cup \set*{q}} = \emptyset \\ 
            \implies &\paren*{E \cap Q_{\veps}(q)} \cup \paren*{E \cap \set*{q}} = \emptyset \\
            \implies &E \cap Q_{\veps}(q) = \emptyset \\
            \implies &q \notin E'.
        \end{align*}
        Since $q$ is arbitrary, we have
        \[
        N_{r}(p) \subseteq \paren*{E'}^{c} \implies N_{r}(p) \subseteq
        \paren*{\overline{E}}^{c} = E^{c} \cap \paren*{E'}^{c},
        \]
        which implies that $p$ is an interior point of $\paren*{\overline{E}}^{c}$. Since $p$ is arbitrary, $\paren*{
        \overline{E}}^{c}$ is open, which implies that $\overline{E}$ is closed by \Cref{cor:ClosedSetComplementIsOpenSet}.
        \item $E$ is closed $\iff E' \subseteq E \iff E \cup E' = E \iff \overline{E} = E$.
        \item Let $F \subseteq X$ be a closed set such that $E \subseteq F$. Let $p \in E'$ be given.
        Then, for any $r \in \R^{+}$, we have
        \[
        E \cap Q_{r}(p) \neq \emptyset \implies F \cap Q_{r}(p) \neq \emptyset,
        \]
        which implies that $p \in F' \subseteq F$. Therefore, we have $E' \subseteq F$.
        Since $E \subseteq F$, we have $\overline{E} = E \cup E' \subseteq F$.
    \end{enumerate}
\end{proof}

\bigskip

\begin{theorem} \label{thm:IsolatedPoints}
    Let $(X, d)$ be a metric space and $E \subseteq X$. Then we have
    \[
    E \setminus E' = \setbuilder*{p \in X}{p \text{ is an isolated point of } E}.
    \]
\end{theorem}

\begin{proof}
    \textbf{($\subseteq$)} Let $p \in E \setminus E'$ be given.
    Since $p \notin E'$, there exists some $r \in \R^{+}$ such that
    \[
    E \cap Q_{r}(p) = \emptyset \implies \paren*{E \cap N_{r}(p)} \setminus \set*{p} = \emptyset.
    \]
    Since $p \in E$ and $p \in N_{r}(p)$, we have
    \[
    E \cap N_{r}(p) = \set*{p},
    \]
    which implies that $p$ is an isolated point of $E$.
    \\[6mm]
    \textbf{($\supseteq$)} Let $p$ be an isolated point of $E$. Then there exists some $r \in \R^{+}$ such that
    \[
    E \cap N_{r}(p) = \set*{p}.
    \]
    Then we have
    \begin{itemize}
        \item $E \cap Q_{r}(p) = \emptyset \implies p \notin E'$.
        \item $p \in E$.
    \end{itemize}
    Therefore, we have $p \in E \setminus E'$.
\end{proof}

\bigskip

\begin{definition} \label{def:Boundary}
    Let $(X, d)$ be a metric space and $E \subseteq X$. The \textbf{boundary} of $E$,
    which is denoted by $\partial E$, is defined by
    \[
    \partial E \coloneqq \overline{E} \cap \overline{E^{c}}.
    \]
\end{definition}